---
title: "Global Trade"
author: "Oamar Gianan"
date: "October 27, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


####### START HERE

```{r load libraries, echo=TRUE, message=TRUE, warning=TRUE}

csvs <- list.files(path = 'csv/', pattern = ".CSV")
csvs <- paste('csv/', csvs, sep = '')
length(csvs)
all_data <- do.call("rbind", lapply(csvs, read_csv))

#Discard duplicate rows

all_data <- all_data[!duplicated(all_data),]
raw_data <- all_data
all_data <- all_data %>% filter(Partner != '...')
all_data <- all_data %>% filter(`Indicator Type` == 'Export' | `Indicator Type` == 'Import')


all_data <- all_data %>% filter(!str_detect(Indicator, 'share'))
all_data <- all_data %>% filter(Partner != 'Unspecified')
all_data <- all_data %>% filter(Partner != 'Other Asia, nes')
all_data <- all_data %>% filter(Reporter != 'Occ.Pal.Terr')
all_data <- all_data %>% filter(Partner != 'Free Zones')
all_data <- all_data %>% filter(Reporter != 'European Union')
all_data <- all_data %>% filter(Reporter != 'World')
all_data <- all_data %>% filter(Partner != 'Bunkers')

all_data <- all_data %>% select(1:11)

library(reshape)
library(reshape)
vec <- names(all_data)[1:5]
vec
all_data <- as.data.frame(all_data)
class(all_data)

all_data <-melt(all_data, id = vec)
names(all_data)[6] <- "Year"
names(all_data)[7] <- "amount"

all_data <- all_data[complete.cases(all_data),]

all_data <- all_data %>% filter(Partner != 'Other Asia, nes' & Reporter != 'Other Asia, nes')

library(readr)
write_csv(all_data, "temp.csv")

all_data <- read_csv("temp.csv")


Reporter <- unique(all_data$Reporter)
Partner <- unique(all_data$Partner)
Countries <- c(Reporter, Partner)
Countries <- unique(Countries)
t <- as.data.frame(Countries)


all_data <- all_data %>% filter(Partner != 'Special Categories' & Reporter != 'Special Categories')

write_csv(all_data, "temp.csv")



all_data <- all_data %>% filter(Partner != 'World' | `Product categories` != "All Products")

write_csv(all_data, "temp.csv")



all_data_categorized <- all_data %>% filter(Partner == 'World')




write_csv(all_data_categorized, 'all_categorized.csv')

all_data <- all_data %>% filter(Partner != 'World')

all_data_im <- all_data %>% filter(`Indicator Type` == 'Import')
all_data_ex <- all_data %>% filter(`Indicator Type` == 'Export')


names(all_data_im)
names(all_data_im)[1] <- 'To'
names(all_data_im)[2] <- 'From'

names(all_data_ex)
names(all_data_ex)[1] <- 'From'
names(all_data_ex)[2] <- 'To'

all_data_ex <- all_data_ex %>% select(1, 2, 6, 7)

all_data_im <- all_data_im %>% select(2, 1, 6, 7)

almost <- as.data.frame(rbind(all_data_im, all_data_ex))
class(almost)
write_csv(almost, "all_data.csv")


```



```{r }
select_year <- 2015
select_percentile <- 95
       


df <- all_data %>% filter(Year == select_year) %>% 
                     filter(amount > quantile(all_data$amount, as.numeric(select_percentile)*.01))  %>% 
                     select(From, To, amount) %>%
                     filter(From %in% Countries)


```

```{r chorddiagram}
              circos.par(start.degree = 90)
              chordDiagramFromDataFrame(df, directional = TRUE,
                                   grid.col = grid_col,
                                   #col = c("#FF000080", "#00FF0010", "#0000FF10"),
                                   #col = c("#E8253C", "#AE1B2D", "#74121E", "#3A090F", "#000000"),
                                   transparency=0.3)
              circos.clear()



```
